### 2019-01-07 thesis_report/theory.tex
Add zigzag and L-systems
Outline of thesis

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ General Physics
%%██████████████████████████████████████████████████████████████████████████
\section{General Physics}
%%--------------------------------------------------------------------------
%%  Spin-orbit coupling
    \subsection{Spin-orbit coupling}
    Rashba spin orbit coupling:
    \begin{equation}
    	H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
    \end{equation}

%%--------------------------------------------------------------------------
%%  Supercurrent
    \subsection{Supercurrent}
    As the field we are describing is 
%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

%%██████████████████████████████████████████████████████████████████████████
%%██ Tight binding
%%██████████████████████████████████████████████████████████████████████████
\section{Tight binding}

%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

%%██████████████████████████████████████████████████████████████████████████
%%██ Topology in solid state physics
%%██████████████████████████████████████████████████████████████████████████
\section{Topology in solid state physics}     The Wikipedia definition of
mathematical topology is as follows: \quote{Topology can be formally defined as
"the study of qualitative properties of certain objects (called topological
spaces) that are invariant under a certain kind of
transformation}\cite{wiki:topology}\\

%%-------------------------------------------------------------------------- 
%% Symmetries     
\subsection{Symmetries}

%%▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓▓

>>>>

% UNCOMMENT SO YOU CAN LINK PAPERS EASILY WITH SUBLIME TEXT
% \bibliography{report}

@@

\section{General Physics}
	\subsection{Boguliubov de Gennes Hamiltonian}

    \subsection{Spin-orbit coupling}
    Rashba spin orbit coupling:
    \begin{equation}
    	H_\text{Rashba} = \alpha (\ky \sigx - \kx \sigy) 
    \end{equation}

    \subsection{Supercurrent}
	The current

	\subsection{Tight binding}

		\subsection{Topology in solid state physics}
		The Wikipedia definition of mathematical topology is as follows:

		\quote{Topology can be formally defined as "the study of qualitative properties of certain objects (called topological spaces) that are invariant under a certain kind of transformation}\cite{noauthor_topology_2018}

			\subsubsection{Symmetries}

\section{Majorana bound states}
	\subsection{General properties}
	\subsection{Decay length}
	\subsection{Topological gap}

\section{Two dimensional platform for Majoranas}
	\subsection{Phase diagram}
	\subsection{Current phase relationship}
	\subsection{Thouless energy}

\section{Scattering matrix formalism}
